### 2021-06-15 paper/appendix_data.tex
New results from clean run with full 30 seeds.

@@

Simplifying the number of contacts, we arrive at the following distributions of the
numbers of contacts by contact type.

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{../figures/results/figures/data/distributions_of_the_number_of_contacts/other_non_recurrent}
    \caption{Number of Non Recurrent Other Contacts}
    \label{n_contacts_other_non_recurrent}
    \floatfoot{\noindent In the model it is sampled every day which of these numbers of
        contacts a person is planned to have. Note that the contact diaries include such high
        values that super spreading events are well possible in our model. The planned number
        of contacts is reduced by policies, seasonality and individual responses to events
        such as receiving a positive rapid test to the number of actual contacts with
        transmission potential. Other contacts include all contacts that are not household
        members, school contacts or work contacts, for example leisure contacts or contacts
        during grocery shopping. We assume that individuals in households with children or
        teachers or retired individuals have additional contacts during school vacations to
        cover things like family visits or travel during vacations. We estimate this to be on
        average 0.5 additional contacts per vacation day.}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{../figures/results/figures/data/distributions_of_the_number_of_contacts/other_recurrent_daily}
    \caption{Number of Daily Recurrent Other Contacts}
    \label{n_contacts_other_daily_recurrent}
    \floatfoot{\noindent Individuals are assigned to groups that are time constant and
        that meet daily. The share of individuals that attend in a way that has transmission
        potential is reduced by policies, seasonality and individual responses to events such
        as receiving a positive rapid test. Other contacts include all contacts that are not
        household members, school contacts or work contacts, for example leisure contacts or
        contacts during grocery shopping.}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{../figures/results/figures/data/distributions_of_the_number_of_contacts/other_recurrent_weekly}
    \caption{Number of Weekly Recurrent Other Contacts}
    \label{n_contacts_other_weekly_recurrent}
    \floatfoot{\noindent Individuals are assigned to up to four groups that are time
        constant and that meet weekly. The share of individuals that attend in a way that has
        transmission potential is reduced by policies, seasonality and individual responses
        to events such as receiving a positive rapid test. Other contacts include all
        contacts that are not household members, school contacts or work contacts, for
        example leisure contacts or contacts during grocery shopping.}
\end{figure}

@@

>>>>

\subsection{The Synthetic Population}

\textcolor{red}{\ldots}

@@

Simplifying the number of contacts, we arrive at the following distributions of the
numbers of contacts by contact type.\comment[id=K]{Put plots into one figure.}

\begin{figure}
    \centering

    \begin{subfigure}[b]{0.25\textwidth}
        \centering

        \includegraphics[width=\textwidth]{../figures/results/figures/data/distributions_of_the_number_of_contacts/other_non_recurrent}
        \caption{Number of Non Recurrent Other Contacts}
        \label{n_contacts_other_non_recurrent}
    \end{subfigure}

    \hfill

    \begin{subfigure}[b]{0.25\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/results/figures/data/distributions_of_the_number_of_contacts/other_recurrent_daily}
        \caption{Number of Daily Recurrent Other Contacts}
        \label{n_contacts_other_daily_recurrent}
    \end{subfigure}

    \hfill

    \begin{subfigure}[b]{0.25\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/results/figures/data/distributions_of_the_number_of_contacts/other_recurrent_weekly}
        \caption{Number of Weekly Recurrent Other Contacts}
        \label{n_contacts_other_weekly_recurrent}
    \end{subfigure}

    \caption{Number of Contacts of the Other Contact Type}
    \label{fig:n_contacts_other}

    \floatfoot{\noindent
        \textit{Note:} Other contacts include all contacts that are not household
        members, school contacts or work contacts, for example leisure contacts or
        contacts during grocery shopping. The planned number of contacts is reduced by
        policies, seasonality and individual responses to events such as receiving a
        positive rapid test to the number of actual contacts with transmission potential.        % non recurrent
        In the model it is sampled every day which of the numbers of non recurrent
        contacts a person is planned to have. Note that the contact diaries include such
        high values that super spreading events are well possible in our model through
        non recurrent other models. We assume that individuals in households with
        children or teachers or retired individuals have additional non recurrent
        contacts during school vacations to cover things like family visits or travel
        during vacations. We estimate this to be on average 0.5 additional contacts per
        vacation day.
        % daily and weekly
        For the recurrent other contacts, individuals are assigned to groups that are
        time constant and that meet daily or weekly. The share of individuals that attend
        in a way that has transmission potential is reduced by policies, seasonality and
        individual responses to events such as receiving a positive rapid test. For
        weekly contacts, individuals are assigned to up to four groups that are time
        constant and that meet weekly. The day on which meetings take place varies
        between groups but stays the same for each group.
    }
\end{figure}

\textcolor{red}{Arbeitsplots auch in eine gemeinsame Graphik packen}

@@

An exception where we do not rely on the data by \cite{Mossong2008} are the household
contacts. Since household are included in the the German microcensus\comment[id=K]{Cite
microcensus} on which we build our synthetic population we simply assume for the
household contact model that individuals meet all other household members every day.

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{../figures/results/figures/data/distributions_of_the_number_of_contacts/household}
    \caption{Number of Household Contacts}
    \label{n_contacts_hh}
    \floatfoot{\noindent
        \textit{Note:} Every individual meets all other household members every day. The
        German microcensus sampled full households such that our synthetic population
        automatically fits population characteristics such as size and age distribution.}
\end{figure}

### 2021-06-15 paper/report.tex
Add number of household contacts.

\begin{figure}
    \centering

@@

@@

The reason lies in the fact that a substantial share of these tests is driven by an
elevated probability to carry the virus, i.e., showing symptoms of CoViD-19 or following
up on a positive test of a household member. The latter is essentially a form of contact
tracing, which has been shown to be very effective \citep{Contreras2021,
Kretzschmar2020}. This is also the reason for why the number of tests performed fall at
the very end of our study period. Falling infection rates mean that there are fewer
events triggering private test demand.\comment[id=HM]{Positive rates along the three
channels might be nice here, if previous comment is not a quant
story}\comment[id=K]{See figure~\ref{fig:share_of_rapid_tests_by_reason_by_infected}}\comment[id=HM]{I think there is a story in here about
risk conditional on past exposure vs. prospective risk in gatherings, but it is too late
to work through it. We might just want to calculate the
probabilities.}\comment[id=K]{I don't understand which probabilities you mean.}

@@

Figure~\ref{fig:workplace_scenarios} shows that with a large fraction of employees receiving tests, testing at the workplace has larger effects than changing requirements to work from home. Whether the share of workers working at the usual workplace is reduced or increased by ten percent hardly has an effect on infection rates. Making testing mandatory twice a week---assuming independet compliance by employers and workers or 95\% each---would have reduced infections by 13\%. Reducing rapid tests offers by employers to the level of March would have increased them by the same amount.

@@

Our analysis\comment[id=J]{The conclusion should be slightly longer and more separated from the rest} has shown that in the transition path to high levels of vaccination and
possibly thereafter, large-scale rapid testing can substitute for some NPIs. This comes
at a fraction of the cost. A day of the winter lockdown in Germany is estimated to have
cost 6.25~billion~Euros \citep{Dorn2020b}.\comment[id=K]{This is a prediction by the ifo
Instute back from March 2020 assuming a 2 month lockdown. I did not find anything citable
that is more recent. I did find
\href{https://www.merkur.de/wirtschaft/lockdown-coronavirus-kosten-deutschland-milliarden-euro-wirtschaft-krise-zr-90231189.html}{A
quote from ifo's Timo Wollmershäuser: „Wir liegen zwischen zwei bis zweieinhalb
Milliarden Euro pro Woche“} for the winter lockdown. That would be much less than
calculated in March.} In early June 2021, retail prices for self-administered rapid tests
are frequently less than 1.5~Euro.\footnote{Cheapest on \href{https://amazon.de}{Amazon}
on June 11th, 2021.}

>>>>

\begin{figure}   % Figure 1
    \centering

@@

\begin{figure}[!tp]   % Figure 2
    \centering

@@

The reason lies in the fact that a substantial share of these tests is driven by an
elevated probability to carry the virus, i.e., showing symptoms of CoViD-19 or following
up on a positive test of a household member. The latter is essentially a form of contact
tracing, which has been shown to be very effective \citep{Contreras2021,
Kretzschmar2020}. This is also the reason for why the number of tests performed fall at
the very end of our study period. Falling infection rates mean that there are fewer
events triggering private test demand.\comment[id=HM]{Positive rates along the three
channels might be nice here, if previous comment is not a quant story}\comment[id=K]{See
figure~\ref{fig:share_of_rapid_tests_by_reason_by_infected}} \comment[id=HM]{I think
there is a story in here about risk conditional on past exposure vs. prospective risk in
gatherings, but it is too late to work through it. We might just want to calculate the
probabilities.}\comment[id=K]{I don't understand which probabilities you mean.}

@@

Figure~\ref{fig:workplace_scenarios} shows that with a large fraction of employees
receiving tests, testing at the workplace has larger effects than changing requirements
to work from home. Whether the share of workers working at the usual workplace is
reduced or increased by ten percent hardly has an effect on infection rates. Making
testing mandatory twice a week---assuming independent compliance by employers and workers
or 95\% each---would have reduced infections by 13\%. Reducing rapid tests offers by
employers to the level of March would have increased them by the same amount.

@@

Our analysis\comment[id=J]{The conclusion should be slightly longer and more separated from the rest} has shown that in the transition path to high levels of vaccination and
possibly thereafter, large-scale rapid testing can substitute for some NPIs. This comes
at a fraction of the cost. A day of the winter lockdown in Germany is estimated to have
cost 6.25~billion~Euros \citep{Dorn2020b}.\comment[id=K]{This is a prediction by the ifo
Instute back from March 2020 assuming a 2 month lockdown. I did not find anything citable
that is more recent. I did find
\href{https://www.merkur.de/wirtschaft/lockdown-coronavirus-kosten-deutschland-milliarden-euro-wirtschaft-krise-zr-90231189.html}{A
quote from ifo's Timo Wollmershäuser: „Wir liegen zwischen zwei bis zweieinhalb
Milliarden Euro pro Woche“} for the winter lockdown} In early June 2021, retail prices
for self-administered rapid tests are frequently less than 1~Euro.\comment[id=HM]{Cheapest on
\href{https://amazon.de}{Amazon} on June 11th, 2021. --- DM 95ct}
